---
title: "Assignment"
author: "Vidipt Vashist MA22M025"
date: "2023-02-12"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Question 2.14

## Input data

```{r}
ratio <- c(1.0, 0.9, 0.8, 0.7, 0.6, 0.5, 0.4, 0.3)
viscosity <- c(0.45, 0.20, 0.34, 0.58, 0.70, 0.57, 0.55, 0.44)
df_14<- data.frame(ratio , viscosity)
```

## a. Scatter plot

```{r}
library(ggplot2) #importing library
ggplot(data =df_14, mapping = aes(x=ratio, y=viscosity)) + geom_point(size = 2) # size of point =3
```

## b. Estimate the prediction equation

```{r}
model_14 = lm(viscosity~ratio)
coefficients(model_14)
```

```{r}
ggplot(data = df_14, mapping= aes(x=ratio, y=viscosity)) + geom_point(size = 2) + geom_smooth(method=lm , se=FALSE)
```

## c. Analysis

#### Summary of model

```{r}
summary(model_14)
```

#### Anova table

```{r}
summary.aov(model_14)
```

```{r}
df(0.01 , 1 , 6)
```

## thus accept null hypothesis Implies There no linear relation.

## R2 value

```{r}
summary(model_14)$r.squared
```

### model explain only 21% so linear relation is not present.

# d. Calculate and plot 95% confidence and prediction band

```{r}
cls<- predict(model_14 , interval ="confidence" , level = 0.95)
cls
```

```{r}
ggplot(df_14, aes(x=ratio, y=viscosity)) + geom_point(size = 2) + geom_smooth(method=lm , se=TRUE) +
labs(title="95% confidence intervals",
       x=" ratio ", y = "viscosity")
```

# Question 2.15

## Input data

```{r}
visco <- c(24.9, 35, 44.9, 55.1, 65.2, 75.2, 85.2, 95.2)
temperature <- c(1.1330, 0.9772, 0.8532, 0.7550, 0.6723, 0.6021, 0.5420, 0.5074)
df <- data.frame(temperature , visco)
df
```

```{r}
# Scatter plot
library(ggplot2)
ggplot(df, aes(x=visco, y=temperature)) + geom_point(size = 3)
```

# a. Estimate the prediction equation

```{r}
model_15 <- lm(temperature~visco)
coefficients(model_15)
```

Regression line

```{r}
ggplot(df, aes(x=visco, y=temperature)) + geom_point(size = 3) + geom_smooth(method=lm , se=FALSE)
```

# b. Analysis of model

```{r}
summary(model_15)
```

```{r}
summary.aov(model_15)
```

```{r}
df(0.001 , 1, 6)
```

## As our F value = 144.6 \> f(0.001, 1 , 6)

## we reject null hypothesis and accept alternate hypothesis which implies there is linear relation

```{r}
summary(model_15)$r.squared
```

# Model explain 96% of variation.

# c. Calculate and plot 95% confidence intervals

```{r}
cls_15<-predict(model_15 , interval="confidence" , level =0.95)
cls_15<-data.frame(cls_15) # Prediction bands in DataFrame
cls_15$temperature<-temperature
cls_15
```

```{r}
ggplot(df, aes(x=visco, y=temperature)) + geom_point(size = 3) +
geom_smooth(method=lm, se=TRUE, fullrange=FALSE, level=0.95) +
labs(title="95% confidence intervals",
       x=" X ", y = "Y")

```

# Question 2.16

## Input Data

```{r}
vol<- c(2084,2084 , 2273, 2273,2273, 2463 ,2463 ,2651 , 2652,2652,2842, 2842,3030,3031,3031,3221,3221,3409,3410,3600,3600,3788,3789,3789,3979,3979,4167,4168,4168,4358,4358,4546,4547
)
pressure <-c(4599,4600,5044,5043,5044,5488,5487,5931,5932,5932,6380,6380,6818,6817,6818,7266,7268,7709,7710,8156,8158,8597,8599,8600,9048,9048,9484,9487,9487,9936,9938,10377,10379
)
df_16 <- data.frame(vol , pressure)
df_16
```

## Scatter Plot

```{r}
ggplot(df_16 , aes(x =vol , y = pressure))+ geom_point(size = 2)

```

## Correlation

```{r}
cor(df_16$pressure , df_16$vol)
```

Very high correlation

## Fitting of model

```{r}
model_16 <- lm(df_16$vol~df_16$pressure)
summary(model_16)
```

### Anova Table

```{r}
summary.aov(model_16)
```

```{r}
df(0.001 , 1 ,31)
```

## We reject null hypothesis implies linear relation.

# R2 value

```{r}
summary(model_16)$r.squared
```

model explain 99% variation

```{r}
ggplot(df_16, aes(x=vol ,y=pressure)) + geom_point(size = 3) + geom_smooth(method=lm, se=TRUE, fullrange=TRUE, level=0.99) +
labs(title="99% confidence intervals",
       x=" X ", y = "Y")


```

# Question 2.17

## Input Data

```{r}
bpoint <- c(199.5,199.3,197.9,198.4,199.4,199.9,200.9,201.1,201.9,201.3,203.6,204.6,209.5,208.6,210.7,211.9,212.2

)
bpressure <- c(20.79,20.79,22.40,22.67,23.15,23.35,23.89,23.99,24.02,24.01,25.14,26.57,28.49,27.76,29.64,29.88,30.06
)
df_17 <- data.frame(bpoint , bpressure)
df_17
```

## Scatter Plot

```{r}
ggplot(df_17 , aes(x =bpoint , y = bpressure))+ geom_point(size = 2)
```

## Corelation value

```{r}
cor(bpoint,bpressure)
```

## Fitting model

```{r}
model_17 <- lm(bpressure ~ bpoint)
summary(model_17)
```

```{r}
coefficients(model_17)
```

```{r}
# Regression line 
ggplot(df_17 , aes(x =bpoint , y = bpressure))+ geom_point(size = 2) + geom_smooth(method=lm , se=FALSE)

```

### Anova Table

```{r}
summary.aov(model_17)
```

```{r}
df(0.001 , 1 , 15)
```

#### Thus we reject null hypothesis.

## R2 value

```{r}
summary(model_17)$r.squared
```

### Model explain 93% of variation

## 95% Interval Estimation

```{r}
cls_16<-predict(model_16 , interval="confidence" , level =0.95)
cls_16<-data.frame(cls_16) # Prediction bands in DataFrame
cls_16
```

```{r}
ggplot(df_17 , aes(x =bpoint , y = bpressure))+ geom_point(size = 2) + geom_smooth(method=lm , se=TRUE) +
labs(title="95% confidence intervals", x=" bpoint ", y = "bpressure")
```

# Question 2.18

## Input Data

```{r}
amount_spend <- c(50.1, 74.1, 19.3,22.9,82.4,40.1,185.9,26.9,20.4,166.2,27,45.6,154.9,5,49.7,26.9,5.7,7.6,9.2,32.4,6.1
 )
returned_impression <-c(32.1, 99.6, 11.7,21.9,60.8,78.6,92.4,50.7,21.4,40.1,40.8,10.4,88.9,12,29.2,38,10,12.3,23.4,71.1,4.4)
firms <-c("Miller Lite","Pepsi","Stroh ","Federal Express","Burger King","Coca-Cola","McDonalds","MCI","DietCola","Ford","Levis","Bud Lite","ATT Bell","Calvin Klein","Wendys","Polaroid","Shasta","Meow Mix","Oscar Meyer","Crest","KibblesNBits"
)
df_18 <- data.frame(amount_spend , returned_impression)
```

### Scatter plot

```{r}
ggplot(df_18 , aes(x =returned_impression , y = amount_spend))+ geom_point(size = 2) 

```

## a. Fit simple linear regression model

```{r}
model_18 <- lm(amount_spend ~ returned_impression)
coefficients(model_18)
```

### Plot Regression line

```{r}
ggplot(df_18 , aes(x =returned_impression , y = amount_spend))+ geom_point(size = 2)  + geom_smooth(method=lm , se=FALSE)
```

## b. Check is their significant relation

H0: B1 = 0

H1: B1 !=0

```{r}
summary.aov(model_18)
```

```{r}
df(.001 , 1, 19)
```

### So there is significant relation. thus reject null hypothesis.

## R2 value

```{r}
summary(model_18)$r.squared
```

### Model explain 42.3% of variation. so there is still a lot of unexplained variation in this model.

## c. Construct 95% confidence interval

```{r}
cls_18 <- predict(model_18 , interval = "confidence" , level =0.95)
cls_18<-data.frame(cls_18)
cls_18$amount_spend <- amount_spend
cls_18$firms <- firms
```

```{r}
ggplot(df_18 , aes(x =returned_impression , y = amount_spend))+ geom_point(size = 2)  + geom_smooth(method=lm , se=TRUE) +
labs(title="95% confidence intervals", x=" returned_impression ", y = "amount_spend")
```
